---
title: "Question 4"
author: "Sumaiya Mehreen"
date: "12/11/2020"
output: html_document
---

```{r}
data<-read.csv("question 4.csv")
data$Method<-as.factor(data$Method)
data$Obsevations1<-cbind(data$Obsevations)
str(data)
install.packages("nopar")
library(nonpar)
install.packages("RVAideMemoire")
library(RVAideMemoire)
```

```{r}
cochrans.q(data$Obsevations1)
```

As p-value > alpha, there is no difference among the methods.

But for further analysis, we can use different ways.

a) Checking the assumption of constant variance(using plot)
```{r}
anova<-aov(data$Obsevations~data$Method,data=data)
summary(anova)
plot(anova)
par(mfrow=c(2,2))
plot(anova)
```

From Residuals vs Fitted and Residuals vs Leverage plots we can see that errors are not parallel to fitted values.We can conclude that variances are not constant.

b) Checking the assumption of constant variance(Using bartlett test)

Ho= Samples have equal variances

```{r}
bartlett.test(data$Obsevations~data$Method,data=data)
```

p-value=0.01947 < alpha=0.05. We reject the null hypothesis. We can conclude that at least one of the sample variances is different.
